---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cryptoQuotes

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/serkor1/cryptoQuotes/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/serkor1/cryptoQuotes/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of cryptoQuotes is to create a unified API access to all known major cryptocurrency exchanges, and preserving the compatibility with libraries such as `quantmod` and `TTR`. 

## Installation

You can install the latest stabl version of cryptoQuotes like so:
``` r
devtools::install_github(
  repo = 'https://github.com/serkor1/cryptoQuotes/',
  ref = 'main'
)
```

You can install the development version of cryptoQuotes like so:

``` r
devtools::install_github(
  repo = 'https://github.com/serkor1/cryptoQuotes/',
  ref = 'development'
)
```

## Example

To get the latest prices on a desired cryptocurrency pair,

```{r example}
## get spotprice on USDT denominated ATOM
spotPrice <- cryptoQuotes::getQuote(
  ticker = 'ATOMUSDT',
  source = 'binance',
  futures = FALSE,
  interval = '30m'
)
```

This `spotPrice` can be passed to the `chartSeries` from `quantmod` directly to chart it with candlesticks.

```{r chartSeries, echo=TRUE, warning=FALSE, message = FALSE}
## chart the spotPrice series
## using quantmod
quantmod::chartSeries(
  x = spotPrice,
  theme = quantmod::chartTheme('black')
)
```
When the `spotPrice` has been charted, the indicators in `quantmod` is directly applicable. See for example `addBBands`

```{r addBBands, echo=TRUE, warning=FALSE, message = FALSE}
## add bollinger bands 
## using quantmod
quantmod::addBBands()
```
