---
title: "Introduction: Cryptocurrency Market Data in R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction: Cryptocurrency Market Data in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse      = TRUE,
  comment       = "#>",
  out.width     = "100%",
  out.height    = "680",
  fig.align     = "center"
)
```

```{r setup, message = FALSE}
library(cryptoQuotes)
```

This `vignette` is a short introduction to [{cryptoQuotes}](https://serkor1.github.io/cryptoQuotes/), for a more extensive introduction on its usecase and limitations please refer to the [wiki](https://github.com/serkor1/cryptoQuotes/wiki).

> **NOTE:** This `vignette` is limited by geolocation due to various country specific
> cryptocurrency laws. The introduction, therefore, is limited to what is available in the US. 

Throughout this `vignette` we will explore the Bitcoin market data using the `Kraken` exchange. All available `tickers` and its notation various across exchangs, so if you are unfamiliar with the exchange specific notation please use the `available_intervals()`-functions,

```{r}
# show a sample of 
# the available tickers
sample(
  x = available_tickers(
    source  = "kraken",
    futures = FALSE
  ),
  size = 5
)
```

These available tickers can be passed into the `ticker`-argument of all the `get_*`-functions with the appropriate `source` and `futures`-argument which, in this case, is `kraken` and `FALSE`.

## Cryptocurrency market data in R

### Open, High, Low, Close an Volume

We will extract the Bitcoin market data in `hourly` intervals, and store it as `BTC`,

```{r}
## extract Bitcoin
## market on the hourly 
## chart
BTC <- get_quote(
  ticker   = "XBTUSDT",
  source   = "kraken",
  futures  = FALSE, 
  interval = "1h"
)
```

```{r, echo=FALSE}
tail(
 BTC 
)
```

The market data can be extracted in different intervals using the `interval`-argument. To see available intervals, the `available_intervals()`-function can be used,

```{r}
## get available
## intervals for OHLC
## on Kraken
available_intervals(
  source  = "kraken",
  type    = "ohlc",
  futures = FALSE
)
```

### Sentiment Data

To put the Bitcoin price action in perspective, an interesting sentiment indicator like the `long` to `short` ratio can be extracted,

```{r}
## extract long-short
## ratio on Bitcoin
## using the hourly chart
LS_BTC <- try(
   get_lsratio(
    ticker   = "XBTUSDT",
    source   = "kraken",
    interval = "1h"
  )
)
```

This gives an `error`. The source of the error is the ticker-naming convention; as the *long-short ratio* is specific to the perpetual futures market, and the current ticker is specific to the spot-market, the endpoint throws an error.

To circumvent this, we can either use perpetual futures throughout the `script`, or modify the `ticker`-argument as follows,

```{r}
## extract long-short
## ratio on Bitcoin
## using the hourly chart
LS_BTC <- get_lsratio(
  ticker   = "PF_XBTUSD",
  source   = "kraken",
  interval = "1h"
)
```

```{r, echo=FALSE}
tail(
 LS_BTC 
)
```

The `ticker` specific to the perpetual futures market can be extracted using the `available_tickers` with `futures = TRUE` as follows,

```{r}
# show a sample of 
# the available tickers
sample(
  x = available_tickers(
    source  = "kraken",
    futures = TRUE
  ),
  size = 5
)
```

## Charting cryptocurrency market data

The Bitcoin market data can be charted using the `chart()`-function, which uses [{plotly}](https://github.com/plotly/plotly.R) as backend,

```{r, fig.alt="cryptocurrency market data with R"}
# candlestick chart with
# volume and Long to Short Ratio
chart(
  ticker = BTC,
  main   = kline(),
  sub    = list(
    volume(),
    lsr(ratio = LS_BTC)
  ),
  options = list(
    dark = FALSE
  )
)
```

### Adding indicators

[{cryptoQuotes}](https://serkor1.github.io/cryptoQuotes/) also acts as an API-client to [{TTR}](https://github.com/joshuaulrich/TTR), and supports most of its functions. We can add Moving Average indicators, and Bollinger Bands to the chart using the `indicator`-argument,

```{r, fig.alt="cryptocurrency market data with R"}
# candlestick chart with
# volume and Long to Short Ratio
chart(
  ticker = BTC,
  main   = kline(),
  sub    = list(
    volume(),
    lsr(ratio = LS_BTC)
  ),
  indicator = list(
    sma(n = 7),
    sma(n = 14),
    sma(n = 21),
    bollinger_bands(
      color = "steelblue"
    )
  ),
  options = list(
    dark = FALSE
  )
)
```

