---
title: "cryptoQuotes: Cryptocurrency Market Data in R"
subtitle: "What happens when Elon Musk Tweets about Dogecoin?"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cryptoQuotes: Cryptocurrency Market Data in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
message = FALSE
)
```

```{r setup}
library(cryptoQuotes)
```

# Introduction

This high-level API-client gives access to cryptocurrency market data, without having to rely on low-level coding using ```httr2``` or ```curl```. All currently listed and actively traded on most of the major cryptocurrencies are available for download.

> **Note:** The library uses xts and zoo under the hood and therefore follows the syntax of base R, and related libraries.

In this vignette we will explore a case study to showcase the capabilities of the library; how was the price action of Dogecoin affected in the minutes after Elon Musk tweeted,

```{r, echo=FALSE, out.width="80%", fig.cap="Tweet by Elon Musk - the timezone is CET.",fig.align='center'}
## include tweet from
## Elon Musk
knitr::include_graphics(
  path = "elonTweet.png"
)
```

# Cryptocurrency Market Analysis in R

Elon Musk tweeted (Well, now he X'ed) about Dogecoin January 14, 06.18 AM (UTC) - and Dogecoin rallied. To determine how fast the markets reacted to his tweets, we could get the market data for Dogecoin in 1 minute intervals the day he tweeeted using the ```getQuotes()```,

```{r, eval = FALSE}
## DOGEUSDT the day
## of the tweet on the
## 1m chart
DOGEUSDT <- cryptoQuotes::getQuote(
  ticker   = 'DOGEUSDT',
  interval = '1m',
  futures  = FALSE,
  from     = '2022-01-14',
  to       = '2022-01-15'
)
```

This returns an object of class `r paste(class(DOGEUSDT),collapse = ' and ')` with `500` rows. To get a closer look on the price action around the tweet hour, we can `subset` the data using the `window()`-function,

```{r}
## extract the hour
## of the tweet
DOGEUSDT <- window(
  x     = DOGEUSDT,
  start = ('2022-01-14 06:00:00'),
  end   = ('2022-01-14 07:00:00')
)
```

This leaves `nrow(DOGEUSDT)` rows, corresponding to a minute by minute price action. We can calculate the price rallying using the 19th row, corresponding to the minute of the tweet. Dogecoin closed at `r DOGEUSDT[19]$Close`, rallying `r paste0(round((DOGEUSDT[19]$Close/DOGEUSDT[19]$Open - 1) * 100,2), '%')`.

## Charting price action with candlesticks

We can illustrate this with candlestick charts using the ```chart()```- and ```kline()```-function, 

```{r, out.width="100%",fig.align='center',fig.height=5}
## chart the
## price action
## using klines
cryptoQuotes::chart(
  chart = cryptoQuotes::kline(
    quote = DOGEUSDT
  ) %>% cryptoQuotes::addVolume(),
  slider = FALSE
)
```

### Charting price action with event lines

To create a, presumably, better visual overview we can add event lines using the  ```addEvents()```-function, which takes a ```data.frame``` of any kind as argument,

```{r}
## 1) create event data.frame
## by subsetting the data
event_data <- as.data.frame(
  zoo::coredata(
    DOGEUSDT[19]
  )
)

## 1.1) add the index 
## to the event_data
event_data$index <- zoo::index(
  DOGEUSDT[19]
)

# 1.2) add event label
# to the data
event_data$event <- 'Elon Musk Tweets'

# 1.3) add color to the
# event label
event_data$color <- 'steelblue'
```

This event data, can be passed into the chart,

```{r, out.width="100%",fig.align='center',fig.height=5}
## 1) create event data.frame
## by subsetting the data
event_data <- as.data.frame(
  zoo::coredata(
    DOGEUSDT[19]
  )
)

## 1.1) add the index 
## to the event_data
event_data$index <- zoo::index(
  DOGEUSDT[19]
)

# 1.2) add event label
# to the data
event_data$event <- 'Elon Musk Tweets'

# 1.3) add color to the
# event label
event_data$color <- 'steelblue'

## 1) chart the
## price action
## using klines
cryptoQuotes::chart(
  chart = cryptoQuotes::kline(
    quote = DOGEUSDT
  )%>% addEvents(
    event = event_data
  ) %>% cryptoQuotes::addVolume(),
  slider = FALSE
)
```


