---
title: "cryptoQuotes: Cryptocurrency Market Data in R"
subtitle: "What happens when Elon Musk Tweets about Dogecoin?"
output: rmarkdown::html_vignette
always_allow_html: true
vignette: >
  %\VignetteIndexEntry{cryptoQuotes: Cryptocurrency Market Data in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  out.width = "100%",
  comment = "#>",
  message = FALSE
)
```

```{css, echo=FALSE}
body, .main-container, .container-fluid {
  max-width: 920px !important; /* or a specific pixel width, e.g., 1200px */
  margin-left: auto !important;
  margin-right: auto !important;
}
```


```{r, message=FALSE}
library(cryptoQuotes)
```

# Introduction

This high-level API-client gives access to cryptocurrency market data, without having to rely on low-level coding using ```httr2``` or ```curl```. All currently listed and actively traded on most of the major cryptocurrencies are available for download.

> **Note:** The library uses xts and zoo under the hood and therefore follows the syntax of base R, and related libraries.

In this vignette we will explore a case study to showcase the capabilities of the library; how was the price action of Dogecoin affected in the minutes after Elon Musk tweeted,

<div align="center">
```{r, echo=FALSE, out.width="80%", fig.cap="Tweet by Elon Musk - the timezone is CET.",fig.align='center'}
## include tweet from
## Elon Musk
knitr::include_graphics(
  path = "elonTweet.png"
)
```
</div>

# Cryptocurrency Market Analysis in R

Elon Musk tweeted (Well, now he X'ed) about Dogecoin January 14, 06.18 AM (UTC) - and Dogecoin rallied. To determine how fast the markets reacted to his tweets, we could get the market data for Dogecoin in 1 minute intervals the day he tweeeted using the ```getQuotes()```,

```{r, eval = FALSE}
## DOGEUSDT the day
## of the tweet on the
## 1m chart
DOGE <- cryptoQuotes::get_quote(
  ticker   = 'DOGEUSDT',
  interval = '1m',
  source   = 'binance',
  futures  = FALSE,
  from     = '2022-01-14',
  to       = '2022-01-15'
)
```

This returns an object of class `r paste(class(DOGE),collapse = ' and ')` with `500` rows. To get a closer look on the price action around the tweet hour, we can `subset` the data using the `window()`-function,

```{r}
## extract the hour
## of the tweet
DOGE <- window(
  x     = DOGE,
  start = ('2022-01-14 07:00:00'),
  end   = ('2022-01-14 08:00:00')
)
```

This leaves `r nrow(DOGE)` rows, corresponding to a minute by minute price action. We can calculate the price rallying using the 19th row, corresponding to the minute of the tweet. Dogecoin closed at `r DOGE[19]$Close`, rallying `r paste0(round((DOGE[19]$Close/DOGE[19]$Open - 1) * 100,2), '%')`.

## Charting price action with candlesticks

We can illustrate this with candlestick charts using the ```chart()```- and ```kline()```-function, 

```{r, fig.align='center', out.height=1000, out.width=1000}
## chart the
## price action
## using klines
cryptoQuotes::chart(
  ticker     = DOGE,
  main       = cryptoQuotes::kline(),
  sub  = list(
    cryptoQuotes::volume()
  ),
  options = list(
    dark = FALSE
  )
)
```

### Charting price action with event lines

To create a, presumably, better visual overview we can add event lines using the  ```addEvents()```-function, which takes a ```data.frame``` of any kind as argument,

```{r}
## 1) create event data.frame
## by subsetting the data
event_data <- as.data.frame(
  zoo::coredata(
    DOGE[19]
  )
)

## 1.1) add the index 
## to the event_data
event_data$index <- zoo::index(
  DOGE[19]
)

# 1.2) add event label
# to the data
event_data$event <- 'Elon Musk Tweets'

# 1.3) add color to the
# event label
event_data$color <- 'steelblue'
```

This event data, can be passed into the chart,

```{r, out.height = 920}
## 1) create event data.frame
## by subsetting the data
event_data <- as.data.frame(
  zoo::coredata(
    DOGE[19]
  )
)

## 1.1) add the index 
## to the event_data
event_data$index <- zoo::index(
  DOGE[19]
)

# 1.2) add event label
# to the data
event_data$event <- 'Elon Musk Tweets'

# 1.3) add color to the
# event label
event_data$color <- 'steelblue'

## 1) chart the
## price action
## using klines
cryptoQuotes::chart(
  ticker     = DOGE,
  event_data = event_data,
  main       = cryptoQuotes::kline(),
  sub  = list(
    cryptoQuotes::volume()
  ),
  options = list(
    dark = FALSE
  )
)
```

