---
title: "Crypto prices in R"
subtitle: "An introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Crypto prices in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cryptoQuotes)
```

This library provides access to recent, and historical, crypto prices from various centralized exchanges using a high level unified API. It supports perpetual futures and spot markets, with varying time intervals.

In this vignette, we will show how the ```ATOMUSDT```-pair can be retrieved from Binance and Kucoin for the futures and spot market, and how these prices can plotted with the most common charts and indicators

### Binance futures market

```{r, eval=FALSE}
## get OHLC data
## from binance futures
## market with daily pips
ATOMUSDT <- cryptoQuotes::getQuote(
  ticker   = 'ATOMUSDTM',
  source   = 'binance',
  futures  = TRUE,
  interval = '15m',
  from     = '2023-10-01',
  to       = '2023-10-02'
)
```

The USDT denominated ATOM, can be charted directly via the `chart`-function, for a quick overview.

```{r, include = FALSE, message=FALSE, echo=FALSE}
### get data from kucoin
### from the internal data set
ATOMUSDT <- cryptoQuotes:::internalTest[[1]][[2]]
```


```{r, out.width="100%",fig.align='center',fig.height=5}
## Create a chart
cryptoQuotes::chart(
  cryptoQuotes::kline(ATOMUSDT, deficiency = FALSE) %>%
    cryptoQuotes::addVolume() %>% 
    cryptoQuotes::addBBands(cols = c('close'))
)
```


### Kucoin spot market

```{r, eval=FALSE}
## get OHLC data
## from Kucoin futures
## market with daily pips
ATOMUSDT <- cryptoQuotes::getQuote(
  ticker   = 'ATOM-USDT',
  source   = 'kucoin',
  futures  = FALSE,
  interval = '15m',
  from     = '2023-10-01',
  to       = '2023-10-02'
)
```

The USDT denominated ATOM, can be charted directly via the `chart`-function, for a quick overview.

```{r, include = FALSE, message=FALSE, echo=FALSE}
### get data from kucoin
### from the internal data set
ATOMUSDT <- cryptoQuotes:::internalTest[[2]][[1]]
```


```{r, out.width="100%",fig.align='center',fig.height=5}
## Create a chart
cryptoQuotes::chart(
  cryptoQuotes::kline(ATOMUSDT, deficiency = FALSE) %>%
    cryptoQuotes::addVolume() %>% 
    cryptoQuotes::addRSI()
)
```
