---
title: "Cryptocurrency Market Data in R"
subtitle: "The cryptoQuotes way"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE
)
```

```{r, message = FALSE}
## load library
library(cryptoQuotes)
```

The main goal of the `cryptoQuotes`-package is to bridge the gap between `R` and the cryptocurrency market data. Its a high-level `API`-client that connects to major cryptocurrency exchanges and their respective public market data endpoints.

In this article we will focus on `price` and `sentiment` data made available by the [Bybit](https://www.bybit.com/en/) exchange.

## Cryptocurrency market data

In this section we will focus on market data from the last 24 hours, on the hourly chart.

### OHLC data

To get `OHLC` data the `get_quote()`-function is the go-to function,

```{r}
## Get the
## SPOT price of 
## Bitcoin on the hourly
BTC <- get_quote(
  ticker  = "BTCUSDT",
  source  = "bybit",
  futures = FALSE,
  interval = "1h",
  from = Sys.Date() - 1
)
```


```{r, echo =FALSE, fig.alt="Cryptocurrency Market Data in R"}
## print table as a kable
## for a neat presentationb
knitr::kable(
  caption = 'Hourly Bitcoin OHLC-V data',
  align = 'lcccc',
  table.attr = "style='width:100%;'",
  x = data.frame(
    cbind(
      Index = paste(tail(zoo::index(BTC))),
      round(tail(zoo::coredata(BTC)),3)
    ),row.names = NULL
  ),
  format = 'html'
)

```

### Sentiment data

One sentiment indicator for Bitcoin is the long-short ratio, which can be retrieved using `get_lsratio()`-function,

```{r}
## Get the
## long-short ratio of 
## Bitcoin on the hourly
LS_BTC <- get_lsratio(
  ticker  = "BTCUSDT",
  source  = "bybit",
  interval = "1h",
  from = Sys.Date() - 1
)
```


```{r, echo =FALSE, fig.alt="Cryptocurrency Sentiment Data in R"}
## print table as a kable
## for a neat presentationb
knitr::kable(
  caption = 'Hourly Bitcoin OHLC-V data',
  align = 'lcccc',
  table.attr = "style='width:100%;'",
  x = data.frame(
    cbind(
      Index = paste(tail(zoo::index(LS_BTC))),
      round(tail(zoo::coredata(LS_BTC)),3)
    ),row.names = NULL
  ),
  format = 'html'
)

```


## Limitations

There is a limit to the amount of market data that can be extracted in one call. The [Bybit](https://www.bybit.com/en/) exchange, for example, has a limit on `1000` rows of data per call in the spot market,

```{r}
## Get the SPOT
## market for over 
## 2000 rows
nrow(
  BTC <- get_quote(
    ticker  = "BTCUSDT",
    source  = "bybit",
    futures = FALSE,
    interval = "30m",
    from = Sys.Date() - 30,
    to   = Sys.Date()
  )
)
```

If you need more data than this, you need to do multiple calls. One such solution is the following,

```{r}
## 1) create date
## sequence
dates <- seq(
  from = as.POSIXct(Sys.Date()),
  by = "-30 mins",
  length.out = 2000
)

## 2) split the sequence
## in multiples of 100
## by assigning numbers
## to each indices of 100
idx <- rep(
  x = 1:2,
  each = 1000
)

## 3) use the idx to split
## the dates into equal parts
split_dates <- split(
  x = dates,
  f = idx
)

## 4) collect all all
## calls in a list
## using lapply
ohlc <- lapply(
  X = split_dates,
  FUN = function(dates){
    
    
    Sys.sleep(1)
    
    cryptoQuotes::get_quote(
      ticker = "BTCUSDT",
      source = "bybit",
      futures = FALSE,
      interval = "30m",
      from = min(dates),
      to   = max(dates)
    )
    
  })

## 4.1) rbind all
## elements
nrow(
  ohlc <- do.call(
    what = rbind, 
    args = ohlc
  )
)
```

> **Note:** For an indepth analysis of the various limitations and workarounds please see the `cryptoQuotes` [wiki](https://github.com/serkor1/cryptoQuotes/wiki) on
> [Github](https://github.com/serkor1/cryptoQuotes)





