---
title: "Cryptocurrency Market Data in R"
subtitle: "The cryptoQuotes way"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE
)
```

```{r, message = FALSE}
library(cryptoQuotes)
```


The main purpose of this library is to bring cryptocurrency market data into ```R```  without having to rely upon low-level coding. This high-level API-client have one main function, ```get_quote()```, which returns cryptocurrency market data with a ```xts```- and ```zoo```-class. The returned objects contains Open, High, Low, Close and Volume data with different granularity, from the currently supported exchanges. In this article we will focus on the Binance exchange, and showcase the different possibilities in the calls.

> **Note:** All exchanges supports spot and perpetual futures market.

## Supported intervals

All supported intervals varies with the exchanges, and market. Here is an example
of supported intervals from the Binance futures market

```{r}
## available intervals
## from Binance futures market
cryptoQuotes::available_intervals(
  source = 'binance',
  futures = TRUE
)
```


The spot market intervals, can be extracted by setting ```futures = FALSE```,

```{r}
## available intervals
## from Binance spot market
cryptoQuotes::available_intervals(
  source = 'binance',
  futures = FALSE
)
```

The ```available_intervals()```-function invisibly returns a character vector, that can be used in, for example, lapply to extract the same cryptocurrency with different intervals. The ```source``` controls the exchange. Here is an example of what is returned using the Kucoin exchange,

```{r, message=FALSE}
## available intervals
## from kucoin spot market
## and its return value
print(
  cryptoQuotes::available_intervals(
    source = 'kucoin',
    futures = FALSE
  )
)
```

## Supported exchanges

The currently supported exchanges can be retrived using the ```available_exchanges()```-function, which also invisibly returns a ```character```-vector,


```{r}
## supported exchanges
## and its return value
exchanges <- cryptoQuotes::available_exchanges()

## print its value
print(
  exchanges
)
```

## Supported tickers

All listed, and active, cryptocurrencies on the supported exchanges are available for extraction using the ```get_quotes()```-function. 

The cryptocurrency tickers varies across exchanges, and within markets for some exchanges. Supported tickers for specific exchanges and markets can be retrieved using the ```available_tickers()```-function,

```{r, eval = FALSE}
## available tickers
## on Binance futures
## market
cryptoQuotes::available_tickers(
  source  = 'binance',
  futures = TRUE 
)
```

> **NOTE:** availableTickers() can't be run here as CRAN, and Github, doesn't allow
> for API calls.

The ```available_tickers()```-function returns a ```character```-vector, sorted alphabetically.

## Cryptocurrency Market Data in R

To get cryptocurrency market data in R, the ```get_quote()```-function is used. Below is an example on how to get
Dogecoin with 1 minute intervals using the Binance exchange,

```{r, eval=FALSE}
## DOGE on the
## 1m chart from the
## spot market
DOGE <- cryptoQuotes::get_quote(
  ticker   = 'DOGE',
  source   = 'binance',
  interval = '1m',
  futures  = FALSE,
  from     = '2022-01-14',
  to       = '2022-01-15'
)
```


```DOGE``` has the ```class``` `r paste(class(DOGE), collapse = ' and ')`, and has the following structure as seen below,


```{r, echo =FALSE}
## print table as a kable
## for a neat presentationb
  knitr::kable(
    caption = 'USDT denominated Dogecoin structure',
    align = 'lcccc',
    table.attr = "style='width:100%;'",
    x = data.frame(
      cbind(
        Index = paste(tail(zoo::index(DOGE))),
        tail(zoo::coredata(DOGE))
      ),row.names = NULL
    ),
    format = 'html'
  )

```

The arguments can be modified according to the application, below is an example of getting ATOM in 15 minutes intervals from the perpetual futures market using the Binance exchange again,

```{r, eval=FALSE}
## ATOMUSDT on the
## 15m chart from the
## futures market
ATOMUSDT <- cryptoQuotes::get_quote(
  ticker   = 'ATOMUSDT',
  source   = 'binance',
  interval = '15m',
  futures  = TRUE,
  from     = '2023-01-01',
  to       = '2023-01-02'
)
```


```{r, echo =FALSE}
## print table as a kable
## for a neat presentation
  knitr::kable(
    caption = 'USDT denominated ATOM structure',
    align = 'lcccc',
    table.attr = "style='width:100%;'",
    x = data.frame(
      cbind(
        Index = paste(tail(zoo::index(ATOM))),
        tail(zoo::coredata(ATOM))
      ),row.names = NULL
    ),
    format = 'html'
  )
```

> **Note:** get_quotes() can't be run here as CRAN, and Github, doesn't allow
> for API calls. The datasets are examples that can be found in the library.
