---
title: "Cryptocurrency Market Data in R"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  message    = FALSE,
  echo       = TRUE, 
  comment    = "#>",
  out.width  = "100%",
  out.height = "620px",
  fig.align  = "center"
)
```

```{r, message = FALSE}
## load library
library(cryptoQuotes)
```

The main goal of the `cryptoQuotes`-package is to bridge the gap between `R` and the cryptocurrency market data. Its a high-level `API`-client that connects to major cryptocurrency exchanges and their respective public market data endpoints.

In this article we will focus on `price` and `sentiment` data made available by the [Kraken](https://www.kraken.com/) exchange.

## Cryptocurrency market data

In this section we will focus on market data from the last 24 hours, on the hourly chart.

### OHLC data

To get `OHLC` data the `get_quote()`-function is the go-to function,

```{r}
## Get the
## SPOT price of 
## Bitcoin on the hourly
BTC <- get_quote(
  ticker   = "BTCUSD",
  source   = "kraken",
  futures  = FALSE,
  interval = "1h",
  from     = Sys.Date() - 1
)
```


```{r, echo = FALSE, fig.alt="Cryptocurrency Market Data in R"}
## print table as a kable
## for a neat presentationb
knitr::kable(
  caption    = 'Hourly Bitcoin OHLC-V data',
  align      = 'lcccc',
  table.attr = "style='width:100%;'",
  x = data.frame(
    cbind(
      index = paste(tail(zoo::index(BTC))),
      round(tail(zoo::coredata(BTC)),3)
    ),
    row.names = NULL
  ),
  format = 'html'
)

```

### Sentiment data

One sentiment indicator for Bitcoin is the long-short ratio, which can be retrieved using `get_lsratio()`-function,

```{r}
## Get the
## long-short ratio of 
## Bitcoin on the hourly
LS_BTC <- get_lsratio(
  ticker   = "PF_XBTUSD",
  source   = "kraken",
  interval = "1h",
  from     = Sys.Date() - 1
)
```


```{r, echo =FALSE, fig.alt="Cryptocurrency Sentiment Data in R"}
## print table as a kable
## for a neat presentationb
knitr::kable(
  caption    = 'Hourly Long-Short Ratio on Bitcoin',
  align      = 'lcccc',
  table.attr = "style='width:100%;'",
  x = data.frame(
    cbind(
      index = paste(tail(zoo::index(LS_BTC))),
      round(tail(zoo::coredata(LS_BTC)),3)
    ),row.names = NULL
  ),
  format = 'html'
)

```

## Limitations

There is a limit to the amount of market data that can be extracted in one call. The [Kraken](https://www.kraken.com/) exchange, for example, has a limit on `5000` rows of data per call in the futures market,

```{r}
## Get the SPOT
## market for over 
## 2000 rows
tryCatch(
  get_quote(
    ticker   = "PF_XBTUSD",
    source   = "kraken",
    futures  = TRUE,
    interval = "5m",
    from     = Sys.Date() - 25,
    to       = Sys.Date()
  ),
  error = function(error) {
    
    error
    
  }
)
```

If you need more data than this, you need to do multiple calls. One such solution is the following,

```{r}
## 1) create date
## sequence
dates <- seq(
  from       = as.POSIXct(Sys.Date()),
  by         = "-5 mins",
  length.out = 10000
)

## 2) split the sequence
## in multiples of 100
## by assigning numbers
## to each indices of 100
idx <- rep(
  x    = 1:2,
  each = 5000
)

## 3) use the idx to split
## the dates into equal parts
split_dates <- split(
  x = dates,
  f = idx
)

## 4) collect all all
## calls in a list
## using lapply
ohlc <- lapply(
  X   = split_dates,
  FUN = function(dates){
    
    Sys.sleep(1)
    
    cryptoQuotes::get_quote(
      ticker   = "PF_XBTUSD",
      source   = "kraken",
      futures  = TRUE,
      interval = "5m",
      from     = min(dates),
      to       = max(dates)
    )
    
  }
)

## 4.1) rbind all
## elements
nrow(
  ohlc <- do.call(
    what = rbind,
    args = ohlc
  )
)
```

> **Note:** For an indepth analysis of the various limitations and workarounds please see the `cryptoQuotes` [wiki](https://github.com/serkor1/cryptoQuotes/wiki) on
> [Github](https://github.com/serkor1/cryptoQuotes)





