---
title: "Interactive Cryptocurrency Charts in R"
subtitle: "The cryptoQuotes way"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  comment = "#>",
  out.width = "100%",
  out.height = "1000",
  fig.align = "center"
)
```

```{r, message = FALSE}
## load library
library(cryptoQuotes)
```

As an `experimental` feature, the `cryptoQuotes`-package has a variety of `chart`-functions built on top of `plotly` and `TTR` to visualize cryptocurrency market data and trading indicators interactively.

Throughout this article we will analyze Bitcoin on the hourly chart called by the `get_quotes`-function,

```{r}
## Get the
## SPOT price of 
## Bitcoin on the hourly
BTC <- get_quote(
  ticker  = "BTCUSD",
  source  = "kraken",
  futures = FALSE,
  interval = "1h",
  from = Sys.Date() - 7
)
```

## Price charts

There are two main price charts. The Japanese candlestick chart, ```kline()```, and the basic OHLC chart, ```ohlc()```, charts. A chart has to be wrapped in the ```chart()```-function.

> All charts comes with `volume` and `bollinger bands` by `default`.

### Candlestick charts

```{r, fig.alt="cryptocurrency charts in R"}
## chart BTC
## with candlesticks
chart(
  ticker = BTC,
  main   = kline()
)
```


### OHLC charts

```{r, fig.alt="cryptocurrency charts in R"}
## chart BTC
## with candlesticks
chart(
  ticker = BTC,
  main   = ohlc()
)
```


> The `chart()`-function comes with various `options` for color deficiency and themes. Use `?chart` for
> further details.

## Charting indicators

All the charts supports various indicators such as `RSI`, `MACD` and `MA`. These can be passed into their respective arguments as follows,

```{r, fig.alt="cryptocurrency charts in R"}
## chart BTC
## with candlesticks
## and various indicators
chart(
  ticker = BTC,
  main   = kline(),
  sub    = list(
    volume(),
    rsi(),
    macd()
  ),
  indicator = list(
    sma(n = 7),
    sma(n = 21),
    bollinger_bands()
  )
)
```


## Charting events

All charts supports passing `event_data`, which are any type of `data.frame`, that can be plotted on the chart. Below is an example of plotting the crossing of the `MA`, 


```{r Locate bullcross}
## Calculate moving averages
## SMA(7) and SMA(10)
BTC$short_SMA <- TTR::SMA(
  x = BTC$close,
  n = 7
)

BTC$long_SMA <- TTR::SMA(
  x = BTC$close,
  n = 21
)

## Determine the cross
## from below
BTC$cross <- as.numeric(
  lag(BTC$short_SMA) < BTC$long_SMA &
    BTC$short_SMA > BTC$long_SMA 
)
```


Based on the `cross` indicator, the `BTC` pair can now be subset, and processed accordingly.


```{r}
## create event data
## and store it as a data.rfrae
event_data <- subset(
  BTC,
  cross == 1
)

# 1.1) Extract the index
# from the event data
index <- zoo::index(
  event_data
)

# 1.2) Convert the coredata
# into a data.frame
event_data <- as.data.frame(
  zoo::coredata(event_data)
)

# 1.3) Add the index into the data.frame
# case insensitive
event_data$index <- index


# 1.4) add events to the data.
# here we use Buys and Sells.
event_data$event <- 'Bull Cross'
event_data$color <- 'darkgray'

```


Finally, the crosses can be plotted using the `chart()` and `addEvents()` functions, like below,

```{r}
## add the events
## the chart, along
## with Moving averages
## and the Bollinger Bands
## in a candlestick chart
chart(
  ticker = BTC,
  main   = kline(),
  indicator = list(
    bollinger_bands(),
    sma(n = 7),
    sma(n = 21)
  ),
  event_data = event_data
)
```


## Limitations

The charting functions are still at an `experimental`-phase as per version `1.3.0`, and might therefore include various bugs of all sizes.
