---
title: "Interactive Cryptocurrency Charts in R"
subtitle: "The cryptoQuotes way"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
library(cryptoQuotes)
```


The ```cryptoQuotes``` library uses ```plotly``` to visualize the quotes interactively.

> **Note:** As per `r paste(Sys.Date())` the charting is still in its experimental
> phase.

There are two main price charts. The Japanese candlestick chart, ```kline()```, and the basic OHLC chart, ```ohlc()```, charts. A chart has to be wrapped in the ```chart()```-function.

# Charting Cryptocurrency with R

For charting the cryptocurrency, we get the ```ATOM``` pair from Binance in 15 minute intervals,

```{r, eval=FALSE}
## ATOM on the
## 15m chart from the
## futures market
ATOM <- cryptoQuotes::get_quote(
  ticker   = 'ATOMUSDT',
  source   = 'binance',
  interval = '15m',
  futures  = TRUE,
  from     = '2023-01-01',
  to       = '2023-01-02'
)
```

## OHLC chart

The basic ohlc chart can be charted by passing the ```ATOM```-pair into the ```ohlc()```-function and then wrap it in ```chart()```

```{r basic OHLC chart, out.width="100%",fig.align='center',fig.height=8}
## simple bar-chart
## without indicators
cryptoQuotes::chart(
  ticker  = ATOM,
  main    = ohlc(),
  options = list(
    dark = TRUE
  )
)
```

## Candlestick chart

The japanese candlestick chart can be charted by passing the ```ATOM```-pair into the ```kline()```-function and then wrap it in ```chart()```

```{r basic kline chart, out.width="100%",fig.align='center',fig.height=8}
## simple kline chart
## without indicators
cryptoQuotes::chart(
  ticker  = ATOM,
  main    = ohlc(),
  options = list(
    dark = TRUE
  )
)
```


# Charting cryptocurrency indicators with R

All the charts supports various indicators such as ```RSI``` and ```Bollinger Bands```. All indicators starts with ```addIndicator```, and can be used with the pipe operator from ```magrittr```.

## RSI and Bollinger Bands

Below is an example of using the ```addRSI()``` and ```addBBands()``` indicators,

```{r basic kline chart with RSI and Bollinger Bands, out.width="100%",fig.align='center',fig.height=8}
## simple kline chart
## without indicators
chart(
  ticker = ATOM,
  main   = kline(),
  indicator = list(
    rsi(),
    bollinger_bands()
  )
)
```


## MACD and Volume

Below is an example of using the ```addMACD()``` and ```addVolume()``` indicators,

```{r basic kline chart with Bollinger Bands and Volume, out.width="100%",fig.align='center',fig.height=8}
## simple kline chart
## without indicators
chart(
  ticker = ATOM,
  main   = kline(),
  indicator = list(
    macd(),
    volume()
  )
)
```


## Charting events

Various events in the financial markets does, undoubtedly, have an impact on the prices. For traders relying on technical analysis one important event is when the short simple moving average (SMA), crosses the long SMA. We can use ```TTR::SMA()``` to calculate the SMA,

```{r Locate bullcross}
## Calculate moving averages
## SMA(7) and SMA(10)
ATOM$short_SMA <- TTR::SMA(
  x = ATOM$Close,
  n = 7,
)

ATOM$long_SMA <- TTR::SMA(
  x = ATOM$Close,
  n = 21,
)

## Determine the cross
## from below
ATOM$cross <- as.numeric(
  lag(ATOM$short_SMA) < ATOM$long_SMA &
    ATOM$short_SMA > ATOM$long_SMA 
)
```


Based on the `cross` indicator, the `ATOM` pair can now be subset, and processed accordingly.


```{r}
## create event data
## and store it as a data.rfrae
event_data <- subset(
  ATOM,
  cross == 1
)

# 1.1) Extract the index
# from the event data
index <- zoo::index(
  event_data
)

# 1.2) Convert the coredata
# into a data.frame
event_data <- as.data.frame(
  zoo::coredata(event_data)
)

# 1.3) Add the index into the data.frame
# case insensitive
event_data$index <- index


# 1.4) add events to the data.
# here we use Buys and Sells.
event_data$event <- 'Bull Cross'
event_data$color <- 'darkgray'

```


Finally, the crosses can be plotted using the `chart()` and `addEvents()` functions, like below,

```{r, out.width="100%",fig.align='center',fig.height=10}
## add the events
## the chart, along
## with Moving averages
## and the Bollinger Bands
## in a candlestick chart
chart(
  ticker = ATOM,
  main   = kline(),
  indicator = list(
    bollinger_bands(),
    sma(n = 7),
    sma(n = 21)
  ),
  event_data = event_data
)
```
