---
title: "Available tickers"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(cryptoQuotes)
```


All tradable tickers on each exchange is supported. The naming convention differs across exchanges, so passing `ATOMUSDT` on the `cryptoQuotes::getQuote` as an argument will not necessarily provide you with the ticker you are looking for.

>***Note:*** Some exchanges uses different tickers for the same pair across markets. So the ticker ATOM-USDT in the spot market might have a different ticker in the perpertual futures market.

To get all tradable assets on the desired market, and exchange, you can use the `cryptoQuotes::availableTickers()` function.


```{r, eval=FALSE}
cryptoQuotes::availableTickers(
  source  = 'kraken',
  futures = TRUE
)
```


> **Note:** the function here is not evaluated as it 
> fails the R-CMD-CHECK on github, and CRAN. The function returns a character
> vector with all available tickers
