---
title: "Dealing with Time Zones"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  message    = FALSE,
  echo       = TRUE, 
  comment    = "#>",
  out.width  = "100%",
  out.height = "620px",
  fig.align  = "center"
)
```

```{r, message = FALSE}
## load library
library(cryptoQuotes)
```

By `default` all data from the `get_*`-family of functions is returned with `Sys.timezone()` and, if not specified otherwise, all `dates` passed into the `from` and `to` parameters are assumed to be `Sys.timezone()` too.

> **NOTE:**
> As the [{pkgdown}](https://github.com/r-lib/pkgdown)-documentation gets built on Github-servers we manually
> specify the timezone of the `from` and `to` parameters.

In this article we will demonstrate the *time zone* aspect of [{cryptoQuotes}](https://github.com/serkor1/cryptoQuotes).

## Open, High, Low, Close and Volume (OHLC-V) with CET

Assume that you are interested in the hourly `Bitcoin` price action from yesterday between 16.00 and 18.00 *central European time* (CET). We start the example by defining the `from` and `to` parameters,

```{r}
# define from
# and to
from <- as.POSIXct(
  x = paste(
    Sys.Date() - 1, "16:00:00"
  ),
  tz = "CET"
)

to <- as.POSIXct(
  x = paste(
    Sys.Date() - 1, "18:00:00"
  ),
  tz = "CET"
)
```

### OHLC-V

As the *time zone* on Github servers are `CET`, the returned OHLC-V data is `UTC` as demonstrated below,

```{r}
## Get hourly
## BTC between
## 16:00 and 18:00 from
## yesterday
xts::tzone(
  BTC <- get_quote(
    ticker   = "BTCUSD",
    source   = "kraken",
    interval = "1h",
    futures  = FALSE,
    from     = from,
    to       = to
  )
)
```

All time zones can be converted using the `xts::tzone()`-function. Below is an example of converting the `BTC` to `CET`,

```{r}
## 1) Change time
## zone to CET
BTC_CET <- BTC
xts::tzone(BTC_CET) <- "CET"
```

Below is table with the original *index* in `UTC` and the converted *index* in `CET`,

```{r, echo=FALSE}
# 1) create a kable
# and print
knitr::kable(
  caption = 'Time zone comparsion',
  align = 'lr',
  table.attr = "style='width:100%;'",
  col.names = c('Original Index', 'Converted Index'),
  x =  cbind(
    paste(zoo::index(BTC)),
    paste(zoo::index(BTC_CET))
  ),
  format = 'html'
)
```

