---
title: "Time Zones"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE
)
```

```{r, message = FALSE}
## load library
library(cryptoQuotes)
```

By `default` all data is returned with `Sys.timezone()` and, if not specified otherwise, all `dates` passed into the `get`-functions are `Sys.timezone()` too.

## Different time zones

### OHLC (Local)

If `from` and `to` are passed as valid `date`-type `characters`, `sys.time()` or `as.POSIXct()` without specifying the `TZ` the returned `xts::index()` is 'as is',

```{r}
## Get hourly
## BTC between
## 20.00 and 22.00 from
## yesterday
BTC_local <- get_quote(
  ticker   = "BTCUSD",
  source   = "kraken",
  interval = "1h",
  futures  = FALSE,
  from     = paste(Sys.Date()-1, "20:00:00"),
  to       = paste(Sys.Date()-1, "22:00:00")
)
```

### OHLC (UTC)

If `from` and `to` are passed as `as.POSIXct()` while specifying the `TZ` the returned `xts::index()` is internally converted,

```{r}
## Get hourly
## BTC between
## 20.00 and 22.00 from
## yesterday
BTC_utc <- get_quote(
  ticker   = "BTCUSD",
  source   = "kraken",
  interval = "1h",
  futures  = FALSE,
  from     = as.POSIXct(paste(Sys.Date()-1, "20:00:00"), tz = "UTC"),
  to       = as.POSIXct(paste(Sys.Date()-1, "22:00:00"), tz = "UTC")
)
```

### Difference

In each case the returned `index` is, alongside the OHLC-V data, different,

```{r,echo=FALSE}
# 1) create a kable
# and print
  knitr::kable(
        caption = 'Time zone comparsion',
    align = 'lr',
    table.attr = "style='width:100%;'",
    col.names = c('BTC_local', 'BTC_utc'),
    x =  cbind(
      paste(zoo::index(BTC_local)),
      paste(zoo::index(BTC_utc))
      ),
    format = 'html'
  )
```


## Changing the time zones

All time zones can be converted using the `xts::tzone()`-function. Below is an example of converting the `BTC` to `UTC`,

```{r}
## 1) Change time
## zone to UTC
## 
## Store BTC_utc in
## a new variable to avoid
## replacing it. Not necessary in the 
## real world - its just for 
## demonstrations
BTC_tzone <- BTC_utc

xts::tzone(BTC_tzone) <- "UTC"
```

```{r,echo=FALSE}
# 1) create a kable
# and print
  knitr::kable(
        caption = 'Time zone comparsion',
    align = 'lr',
    table.attr = "style='width:100%;'",
    col.names = c('Original Index', 'Converted Index'),
    x =  cbind(
        paste(zoo::index(BTC_utc)),
        paste(zoo::index(BTC_tzone))
      ),
    format = 'html'
  )
```

The converted time zones now match the original `argument`-input in `BTC_utc`.

