---
title: "Converting XTS and ZOO objects"
subtitle: "What about data integrity?"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE
  )
```

```{r, message = FALSE}
library(cryptoQuotes)
```

If you want to use the simplicity of ```tidverse``` or the power of ```data.table```, the ```xts```-object can be easily converted.

However, its important to maintain data integrity, especially, if the date and timezone is important for you.

## Converting xts and zoo to tibble

Converting to ```tibble``` requires a few steps to achieve the same data structure as the ```xts```,

```{r tibble}
# 1) load pipe
library(magrittr)

# 2) convert to tibble
# using as_tibble
tbl <- tibble::as_tibble(
  x = cbind(
    Index = zoo::index(ATOMUSDT),
    zoo::coredata(ATOMUSDT)
  )
) %>% dplyr::mutate(
  Index = lubridate::as_datetime(
    Index
  )
)

# 3) head data
head(tbl, 3)
```

## Converting xts and zoo to data.table

Converting to ```data.table``` is straightforward as ```as.data.table()``` handles everything under the hood,

```{r data.table}
# 1) convert to data.table
# using as.data.table
DT <- data.table::as.data.table(
  ATOMUSDT
) 

# 2) set column name to upper
colnames(DT)[1] <- 'Index'

# 3) head data
head(DT, 3)
```


## Checking data integrity

### Checking date integrity

It is important that the date.time has not been converted to a different timezone in the process, without explicitly coding it as such,

```{r}
# 1) store date.time objects
time_objects <- list(
  tbl = tbl$Index,
  DT  = DT$Index
)

# 2) check if they are all equal
all(
  sapply(
    time_objects,
    function(x) {
      
      setequal(
        x = x,
        y = zoo::index(ATOMUSDT)
        )
      
    }
  )
)
```

### Checking OHLCV values

It goes without saying that ```R```-functions wouldn't tamper with the order of the data during conversion without a warning in the documentation, but nonetheless for the sake of argument, we will check the OHLCV values,

```{r}
# 1) store price objects
# Open price here
open_price <- list(
  tbl = tbl$Open,
  DT  = DT$Open
)

# 2) check if they are all equal
all(
  sapply(
    open_price,
    function(x) {
      
      setequal(
        x = x,
        y = ATOMUSDT$Open
        )
      
    }
  )
)

```


## Why even convert?

Even though numerical operations on ```xts```-objects are lightning fast (12% faster than ```data.table```), it comes with a cost; it doesn't support ```factors``` or ```characters```.

Converting the ```xts```-object is a simple and trivial process, and simplifies grouped operations in a verbose manner.

