---
title: "Quantmod and TTR"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE, include=FALSE}
library(cryptoQuotes)
```

### Introduction

The ```cryptoQuotes``` package provides access to most major cryptocurrency exchanges around the world and it uses ```xts``` and ```zoo``` such that it seamlessly works with powerful packages like ```quantmod``` and ```ttr```.

### Charting using quantmod

To demonstrate the interoperability between ```cryptoQuotes``` and ```quantmod```, we extract data from Binance futures market on USDT denominated ATOM

```{r, eval=FALSE}
## load USDT denominated ATOM
## with hourly intervals
## for September
ATOMUSDT <- cryptoQuotes::getQuote(
  ticker = 'ATOMUSDT',
  source = 'binance',
  futures = TRUE,
  interval = '1d',
  from = '2023-01-01',
  to   = '2023-01-11'
)
```

> **Note:** by default, the ```getQuote``` returns an UTC ```index``` which may trigger a warning depending on your timezone.

```{r, eval=TRUE, include=FALSE}
ATOMUSDT <- subset(
  cryptoQuotes::ATOMUSDT,
  cryptoQuotes::ATOMUSDT$exchange == 1 & cryptoQuotes::ATOMUSDT$market == 1
)[,1:5]
```


The ```getQuote``` returns Open, High, Low, Close and Volumes which can be visualized using ```chartSeries``` from ```quantmod``` without further programming.

```{r}
## head data
head(
  ATOMUSDT
)
```

We can pass ```ATOMUSDT``` directly into the ```chartSeries``` and adding bollinger bands indicators using ```quantmod::addBBands```

```{r, out.width="100%",fig.align='center',fig.height=5}
## chart the spotAtom
## with candlesticks
quantmod::chartSeries(
  x     = ATOMUSDT,
  theme = quantmod::chartTheme('white')
)
quantmod::addBBands(n = 2)
```

