---
title: "Cryptocurrency Market Data with Quantmod and TTR"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE
)
```

```{r setup, eval=TRUE, include=FALSE}
library(cryptoQuotes)
```


```cryptoQuotes``` were built to be interoperable with the powerful packages ```quantmod``` and ```TTR```. Here we use an example with ```ATOMUSDT```,

```{r, eval=FALSE}
## load USDT denominated ATOM
## with hourly intervals
## for September
ATOM <- cryptoQuotes::get_quote(
  ticker = 'ATOMUSDT',
  source = 'binance',
  futures = TRUE,
  interval = '15m',
  from     = '2023-01-01',
  to       = '2023-01-02'
)
```

## Cryptocurrency and Quantmod

### Charting Cryptocurrency with Quantmod

The ```ATOMUSDT``` can be passed directly into the ```quantmod::chartSeries()```-function with, if desired, the relevant technical indicators. Pass ```quantmod::addBBands()``` and ```quantmod::addMACD``` into the ```TA```-argument, to add Bollinger Bands and Moving Average Convergence Divergence (MACD) indicators,

```{r, out.width="100%",fig.align='center',fig.height=5}
## chart the spotAtom
## with a candlestick
## chart with Bollinger Bands
## and MACD indicators
quantmod::chartSeries(
  x = ATOM,
  theme = quantmod::chartTheme("white"),
  TA = c(
    # Add Bollinger Bands
    quantmod::addBBands(),
    
    # Add MACD
    quantmod::addMACD()
  )
) 

```


### Locating Peaks with Quantmod

```{r, out.width="100%",fig.align='center',fig.height=5}
# 1) find peaks
# using a small threshold;
peak_idx  <- min(
  quantmod::findPeaks(
  ATOM$Close,
  thresh = 0.022
  )
)

# 2) add to main to main
# chart
quantmod::addLines(
  h = ATOM[peak_idx]$Close,
  overlay = TRUE,
  col     = 'steelblue1'
  )
```



> **NOTE:** quantmod only supports daily interals and, therefore, functions like ```allReturns()``` needs to be modified.


## Cryptocurrency and TTR

For Artificial Intelligence applications, like price prediction, where the ```numeric``` value of the indicators are needed, the indicators from ```TTR``` can be calculated and added to the returned data from the ```cryptoQuotes::get_quote()```-function. ```TTR::BBands()``` is one of such indicators that some traders use as buy and sell signals, these can be added the following way,

```{r}
# 1) calculate
# Bollinger Bands
indicator <- TTR::BBands(
  quantmod::HLC(ATOM)
)

# 2) add to the 
# cryptocurrency quote
ATOM <- cbind(
  ATOM, 
  indicator
)

# 3) calculate
# the distance of the
# closing Price and upper band
ATOM$distance <- (ATOM$up - ATOM$Close)^2
```

The resulting indicator can be fit using, for example, the ```lm()```-function to determine how the distance affects the next closing price.

```{r}
# 1) fit a simple
# model using the distance
# to the upper band and
# lagged closing price
# as predictors
summary(
  lm(
    ATOM$Close ~ xts::lag.xts(ATOM$Close) + xts::lag.xts(ATOM$distance)
  )
)
```

> **NOTE:** In case you werent awar:, this is not financial advise. Its merely a simple demonstration of the available applications.
