---
title: "Cryptocurrency Market Data with quantmod and TTR"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  message    = FALSE,
  echo       = TRUE, 
  comment    = "#>",
  out.width  = "100%",
  out.height = "620px",
  fig.align  = "center"
)
```

```{r, message=FALSE}
## load libraries
library(cryptoQuotes)
```

The `cryptoQuotes` were built with `quantmod` and `TTR` in mind. To demonstrate how `cryptoQuotes` works with these packages, we will use the following data,

```{r}
## Get daily 
## Bitcoin from 
## the spot market
BTC <- get_quote(
  ticker  = "BTCUSD",
  source  = "kraken",
  futures = FALSE,
  interval= "1d",
  from    = "2024-01-01"
)
```

## Cryptocurrency and quantmod

The `BTC` can be passed into the charting functions, or be used in the `quantmod::tradeModel()`-functions.

### Building Cryptocurrency Trade Models

Below is an example on how to use the `quantmod::tradeModel` with `BTC`,


```{r}
## 1) specify
## the model
BTC_model <-  quantmod::specifyModel(
  quantmod::Next(quantmod::OpCl(BTC)) ~ quantmod::Lag(quantmod::OpHi(BTC),0:3)
  )

## 2) build the
## model
built_model <-  quantmod::buildModel(
  x = BTC_model,
  method ='lm',
  training.per = range(head(zoo::index(BTC), 10))
  )

## 3) trade the model
quantmod::tradeModel(built_model,leverage=2)
```

### Charting Cryptocurrency with quantmod

```{r}
## chart the
## BTC with candlesticks
## and Bollinger BAnds
quantmod::chartSeries(
  x = BTC,
  type = "candlesticks",
  TA = c(
    quantmod::addBBands()
  )
)
```

## Cryptocurrency and TTR

Below is an example on how to use the `BBands()`-function from the `TTR`-package,

```{r}
# 1) calculate
# Bollinger Bands
indicator <- TTR::BBands(
  quantmod::HLC(BTC)
)

# 2) add to the 
# cryptocurrency quote
BTC <- cbind(
  BTC, 
  indicator
)
```

```{r, echo =FALSE, fig.alt="Cryptocurrency Market Data in Quantmod"}
## print table as a kable
## for a neat presentationb
knitr::kable(
  caption = 'Bitcoin with Bollinger Bands using TTR',
  align = 'lccccccccr',
  table.attr = "style='width:100%;'",
  x = data.frame(
    cbind(
      Index = paste(tail(zoo::index(BTC))),
      round(tail(zoo::coredata(BTC)),3)
    ),row.names = NULL
  ),
  format = 'html'
)

```
