---
title: "introduction"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cryptoQuotes)
```

### introduction

The ```cryptoQuotes``` package provides access to most major cryptocurrency exchanges around the world, and it uses ```xts``` and ```zoo``` such that it seamlessly works with ```quantmod``` and ```ttr```.


### binance spot market

```{r}
## load USDT denominated ATOM
## with hourly intervals
## for September
spotAtom <- getQuote(
  ticker   = 'ATOMUSDT',
  source   = 'binance',
  futures  = TRUE,
  interval = '1h', 
  from     = '2023-09-01',
  to       = '2023-09-08'
)
```

> **Note:** by default, the ```getQuote``` returns an UTC ```index``` which may trigger a warning depending on your timezone.

The ```getQuote``` returns Open, High, Low, Close and Volumes which can be visualized using ```chartSeries``` from ```quantmod``` without further programming.

```{r, message=FALSE,fig.width=6,fig.height=6,fig.asp=TRUE,fig.align='center'}
## chart the spotAtom
## with candlesticks
quantmod::chartSeries(
  x     = spotAtom,
  theme = quantmod::chartTheme('white')
)
```

### kucoin futures market

The tickers and intervals from the various exchanges varies, and is dependent on the ```API```. To check get a list of available tickers, we can use ```availableTickers```

```{r}
## list available
## tickers on kucoin futures
## market
head(availableTickers(
  source = 'kucoin',
  futures = TRUE
))
```


Our ticker of interst is, for example ,```XBTUSDTM```. It might be interesting to look at different intervals which, again, may differ from exchange to exchange. To get an overview of available intervals we use the ```availableIntervals``` function.

```{r}
## get available
## tickers on kucoin
availableIntervals(
  source = 'kucoin',
  futures = TRUE
)
```


We will look at the ```30m``` intervals, and grab the latest values as possible. To achieve this, we leave ```from``` and ```to``` as ```NULL```

```{r}
## extract XTBUSDTM
## from kucoin with
## 30m intervals
futuresBTC <- getQuote(
  ticker   = 'XBTUSDTM',
  interval = '30m',
  futures = TRUE,
  source = 'kucoin' 
)
```

The ```futuresBTC``` can be charted using ```quantmod``` again, as below,

```{r, message=FALSE,fig.width=6,fig.height=6,fig.asp=TRUE,fig.align='center'}
## chart the futuresBTC
## with candlesticks
quantmod::chartSeries(
  x     = futuresBTC,
  theme = quantmod::chartTheme('white')
)
```


The chart can be extended further with various indicators such as the moving average convergence divergence (MACD).


```{r, message=FALSE,fig.width=6,fig.height=6,fig.asp=TRUE,fig.align='center'}
## chart the futuresBTC
## with candlesticks
quantmod::addMACD()
```
